Argennon: A Scalable Smart Contract Platform

### 2021-07-12 tex/sections/argon.tex
Remove Argon chapter
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

@@

\begin{lstlisting}[frame=TB, float, title=Argon contracts are static classes,label={lst:code1}]
// A contract is a static class and all its methods are automatically static.
contract MirrorToken {
    private SimpleToken token;
    private SimpleToken reflection;

    // `initialize` is a special static method that is called by the AVM after the code of a contract
    // is stored in the AVM code area. It can not be called after that.
    initialize(double supply1, double supply2) {
        // `new` does not create a new smart contract. It just makes an ordinary object.
        token = new SimpleToken(supply1);
        reflection = new SimpleToken(supply2);
    }

@@

public static class Math {
    public double sqrt(double x) {
        return // calculate square root of x
    }
}

>>>>

\lstset{
    language=Java,
    morekeywords={main, initialize, constructor, external, virtual, map, account, signature, overrides, is, string},
    basicstyle=\small\sffamily,
    columns=fullflexible,
%   keywordstyle=\bfseries,
    breaklines=true,
    showstringspaces=false,
    mathescape
}

@@

\begin{lstlisting}[frame=TB, float, title=Argon contracts are static classes,label={lst:code1}]
// .
public class MirrorToken {
    private SimpleToken token;
    private SimpleToken reflection;

    // `initialize` is a special static method that is called by the AVM after the code of a contract
    // is stored in the AVM code area.
    public static void initialize(double supply1, double supply2) {
        // `new` does not create a new smart contract. It just makes an ordinary object.
        token = new SimpleToken(supply1);
        reflection = new SimpleToken(supply2);
    }
    // `main` is the only method of the application (i.e. smart contract) that can be called by other
    // applications. Every application should have exactly one main method defined in a class.
    // Alternativly the keyword `dispatcher` could be used instead of `main`.
    public static RestResponse main(RestRequest arg) {
        if (arg.pathMatches("\balances\{user}")) {
            account sender = arg.getParameter<account>("user");
            if (arg.operationIsPUT()) {
                verify(arg.toMessage(), sender, arg.getParameter<signature>("sig"));
                token.transfer(sender, recipient, amount);
                reflection.transfer(recipient, sender, Math.sqrt(amount));
            } else if (arg.operationIsGET()) {
            } else {
            }
        }
        arg.operationIsGET();
        arg.operationIsPUT();
        arg.getParameter<address>("user")
    }

@@
